---
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    css: styles_flex.css
params: 
    set_title: ""
title: "`r params$set_title`"
---



```{r setup, include=FALSE}
library(flexdashboard)
library(rAmCharts)
library(manipulateWidget)
library(DT)
library(fbAntares)
library(shiny)
```

```{r Fonction plot}

vizModelReal <- function(data, combi, hour, dayType, 
                         xlim = xlim, ylim = ylim) {
  
  column(12,
         combineWidgets(
           ncol = 2,
           list = lapply(1:nrow(combi), function(X) {
             graphFlowBased2D(data, combi[X, 1], combi[X, 2], hour = hour,
                              dayType = dayType)
           }), height = "100%", width = "100%")
  )
}

```


Errors
=====================================

```{r, echo = FALSE, eval = TRUE}
data_error <- dta[idDayType == dayType, .SD, .SDcols = c("idDayType", "Period", "error1", "error2")]

```

### Table
```{r}
data_render <- copy(data_error)
setnames(data_render, c("error1", "error2"), c("Inf error", "Sup error"))
knitr::kable(data_render)
```

### Histogram
```{r}

combineWidgets(
  plot(amHist(x = data_error$error1, main = "Inf error", export = T, xlab = "Inf error")),
  plot(amHist(x = data_error$error2, main = "Sup error", export = T, xlab = "Sup error"))
)
```


Hour 1 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 1]
hour <- 1
```

### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


<!-- ### BE/FR -->
<!-- ```{r} -->
<!-- graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType) -->
<!-- ``` -->

<!-- ### DE/FR -->
<!-- ```{r} -->
<!-- graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType) -->
<!-- ``` -->

<!-- Row {data-height=650} -->
<!-- ------------------------------------------------------------------ -->
<!-- ### BE/NL {.no-padding} -->
<!-- ```{r} -->
<!-- graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType) -->
<!-- ``` -->


<!-- ### DE/NL -->
<!-- ```{r} -->
<!-- graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType) -->
<!-- ``` -->

Hour 2 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 2]
hour <- 2
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------


```{r}
vizModelReal(data, combi, hour, dayType)
```

Hour 3 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 3]
hour <- 3
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------


```{r}
vizModelReal(data, combi, hour, dayType)
```



Hour 4 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 4]
hour <- 4
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 5 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 5]
hour <- 5
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------
```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 6 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 6]
hour <- 6
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------
```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 7 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 7]
hour <- 7
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```



Hour 8 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 8]
hour <- 8
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 9 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 9]
hour <- 9
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 10 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 10]
hour <- 10
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```



Hour 11 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 11]
hour <- 11
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 12 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 12]
hour <- 12
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 13 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 13]
hour <- 13
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------


```{r}
vizModelReal(data, combi, hour, dayType)
```



Hour 14 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 14]
hour <- 14
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 15 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 15]
hour <- 15
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------


```{r}
vizModelReal(data, combi, hour, dayType)
```

Hour 16 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 16]
hour <- 16
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 17 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 17]
hour <- 17
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 18 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 18]
hour <- 18
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 19 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 19]
hour <- 19
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 20 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 20]
hour <- 20
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```

Hour 21 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 21]
hour <- 21
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```

Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```

Hour 22 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 22]
hour <- 22
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 23 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 23]
hour <- 23
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


Hour 24 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[Period == 24]
hour <- 24
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

```{r}
vizModelReal(data, combi, hour, dayType)
```


